Road Segment Prioritization for Bicycle Infrastructure

### 2020-11-20 README.Rmd
Minor typo fix

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# this doesn't work because R project for code is in a different path to R project for paper (relative paths inside code won't work)
# source("R/_1.0_get_flow_data.R")
```

@@

```{r desirefacetcycling, fig.cap="Current and Potential Cycling Demand", out.width="75%", fig.show='hold', echo=FALSE}
knitr::include_graphics("data/Manchester/Plodesire_facet_cycling.png")
```

>>>>

```{r echo=FALSE, results='hide', message=FALSE, warning=FALSE}
# this doesn't work because R project for code is in a different path to R project for paper (relative paths inside code won't work)
source("R/_1.0_get_flow_data.R")
```

@@

```{r desirefacetcycling, fig.cap="Current and Potential Cycling Demand", out.width="75%", fig.show='hold', echo=FALSE}
knitr::include_graphics("data/Manchester/Plots/desire_facet_cycling.png")
```
